Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-14 SDSS-2023/testing-charts-accuracy.qmd

@@

@@

-

@@

Question for Ed: If we compare a full sample to a split sample, do we still want to weight these 'equally'?

Analysis should be done using the 'survey' package and weights should be taken into account.

@@

-

>>>>

## Respondents

Description of respondents -- \# of respondents in each round, broad overview of demo characteristics(?), raw sample size and effective sample size

@@

-   By accuracy vs by behavior (zooming, time spent, etc.)

@@

@@

@@

-   Studying how viewers interact with charts can be done in a survey, and more expansive work on this topic should be completed to understand how the general public interacts with and understands charts.
